% Write your Multi objective criteria and Enginering standards here
%\chapter{Multi objective criteria and Engineering Standards}
\label{Individual Contribution Statement} % If you need a label for this chapter
\thesisspacing % Do not change - required

% Example text
%\textbf{We confirm that the contributions described below accurately represent our role in this research.}
%%\vspace{1cm}
%%\noindent\textbf{Name:} [Your Full Name]  \\
%%\textbf{Signature:} \underline{\hspace{5cm}}  \\
%%\textbf{Date:} [DD/MM/YYYY]  
%%
%%
%%\textbf{Signatures:}
%\renewcommand{\arraystretch}{2} % Increases row height
%\begin{table}[ht]
%    \centering
%    \begin{tabular}{|l|c|m{3cm}|m{4cm}|} % Adjust column widths
%        \hline
%        \textbf{Name and Surname} & \textbf{Student ID} & \textbf{Date} & \textbf{Signature} \\
%        \hline
%        [Name Surname] & [ID] &  &  \\
%        \hline
%        [Name Surname] & [ID] &  &  \\
%        \hline
%        [Name Surname] & [ID] &  &  \\
%         \hline
%        [Name Surname] & [ID] &  &  \\
%         \hline
%        [Name Surname] & [ID] &  &  \\
%        \hline
%    \end{tabular}
%\end{table}
%
%
%
%

This Interim Report/Graduation Project is the result of a collaborative research effort by \textbf{Project Group}, consisting of \textbf{Kürşat Döşkaya,Kenan Selçuk,Burak Uğur}. While the research was conducted as a team, each member contributed distinctively to different aspects of the study.

\section*{Team Contributions}
Team members contributed in the following ways:
\begin{itemize}
    \item \textbf{[Kürşat Döşkaya]}: Contributed to the establishment of the system in the simulation environment, PLC connections and modeling stages. Provided program integration. Also took part in the evaluation and analysis section.
    \item \textbf{[Kenan Selçuk]}: Examined the studies and approaches done so far. Compared the proposed approaches with the approaches in the project. Contributed to the creation of the mathematical model of the engine. Made a program suggestion.
    \item \textbf{[Burak Uğur]}: Researched engineering standards and tested the compliance of the current project with the related engineering standards. Also, researches were found on the limitations of the study and future approaches.
\end{itemize}

Throughout the research process, we collaborated closely, exchanging ideas, refining methodologies, and integrating our findings into a cohesive study. While responsibilities were divided, all major decisions were made collectively, ensuring the integrity and coherence of the final dissertation.
%\vspace{5mm}

\clearpage
\section*{Signatures}
\textbf{We confirm that the contributions described above accurately represent our role in this research.}
%\vspace{1cm}
%\noindent\textbf{Name:} [Your Full Name]  \\
%\textbf{Signature:} \underline{\hspace{5cm}}  \\
%\textbf{Date:} [DD/MM/YYYY]  
%
%
%\textbf{Signatures:}
\renewcommand{\arraystretch}{2} % Increases row height
\begin{table}[http]
    \centering
    \begin{tabular}{|l|c|m{3cm}|m{4cm}|} % Adjust column widths
        \hline
        \textbf{Name and Surname} & \textbf{Student ID} & \textbf{Date} & \textbf{Signature} \\
        \hline
        [Kürşat Döşkaya] & [040200512] & [29.04.2025] & [+]\\
        \hline
        [Kenan Selçuk] & [040200509] & [29.04.2025] & [+]\\
        \hline
        [Burak Uğur] & [040170140] & [29.04.2025] & [+]\\
         \hline
    \end{tabular}
\end{table}
%
%
%
%
%
